Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-10-25 ms.Rnw
Made setting model parameters more explicit

      # Simulate from the fitted version of Model 3
      h3_sims <- simulate(
        h3Spat, nsim = h3_nsim, format = 'data.frame'
      )

@@

@@

mod3_aic <- 2 * mod3_n_params - 2 * mod3_eval_res$ll
mod3_eval_res$subset_aic <- 2 * mod3_n_params - 2 * mod3_eval_res$subset_ll

@@

\begin{tabular}{|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3}
\\
\hline
\hline
\multirow{2}{*}{Log-likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  $\Sexpr{myround(mod3_eval_res$ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(h2_fit$leeFit_ll, 1)}$) &
  ($\Sexpr{myround(max(lee3_results[["all_ll_evals"]]), 1)}$)\footnotemark[2]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ &
  $\Sexpr{as.character(mod2_n_params)}$ &
  $\Sexpr{as.character(mod3_n_params)}$ \\
 Fit Parameters &
 (\Sexpr{as.character(mod1_lee_n_params)}) &
 ($\Sexpr{as.character(h2_fit$leeFit_n_params)}$) &
 ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ &
  $\Sexpr{myround(mod2_aic, 1)}$ &
  $\Sexpr{myround(mod3_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(mod2_lee_aic, 1)}$) &
  ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[2]
\\
\hline
\thead{Log-ARMA(2,1) \\ Log-likelihood} &
  $\Sexpr{myround(ARMA_benchmarks$m1, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m2, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m3, 1)}$
\\
\hline
\end{tabular}
\caption{\label{tab:likes}Log-likelihood values for each models compared to their ARMA benchmarks.
Values in parenthesis are corresponding values using \citet{lee20} parameter estimates.  $\textsuperscript{1}$The reported likelihood is an upper bound of the likelihood of the \citet{lee20} model. $\textsuperscript{2}$\cite{lee20} fit Model~3 to a subset of the data (March 2014 onward, excluding data from Ouest in 2015-2016).
On this subset, their model has a likelihood of $\Sexpr{myround(max(lee3_results$sub_ll_evals), 1)}$.
On this same subset, our model has a likelihood of $\Sexpr{myround(mod3_eval_res$subset_ll, 1)}$.
See Sec.~S5 of the supplement material for more details on estimating the likelihood of the \cite{lee20} models.
}
\end{table}

@@

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/h3_bpf_end_states.rds")) {
  h3_bpf_end_states <- readRDS("model3/run_level_3/h3_bpf_end_states.rds")
} else {
  h3_bpf_end_states <- bake(
    file = paste0("model3/", rl_dir, "h3_bpf_end_states.rds"),
    expr = {
      h3_bpf <- bpfilter(h3Spat, Np = NP_BPF, block_size = 1, save_states = TRUE)
      ss <- h3_bpf@saved.states
      ss[[length(ss)]]
    },
    timing = FALSE
  )
}

@@

      # Get "noVacc" scenario parameters
      h3_S0_par <- get_model3_vacc_scenario_params(scenario = "noVacc")
      coef(h3Spat)[names(h3_S0_par)] <- h3_S0_par

@@

      # Get "noVacc" scenario parameters
      h3_V1_par <- get_model3_vacc_scenario_params(scenario = "2dep")
      coef(h3Spat)[names(h3_V1_par)] <- h3_V1_par

@@

      # Get "noVacc" scenario parameters
      h3_V2_par <- get_model3_vacc_scenario_params(scenario = "3dep")
      coef(h3Spat)[names(h3_V2_par)] <- h3_V2_par

@@

      # Get "noVacc" scenario parameters
      h3_V3_par <- get_model3_vacc_scenario_params(scenario = "slowNation")
      coef(h3Spat)[names(h3_V3_par)] <- h3_V3_par

@@

      # Get "noVacc" scenario parameters
      h3_V4_par <- get_model3_vacc_scenario_params(scenario = "fastNation")
      coef(h3Spat)[names(h3_V4_par)] <- h3_V4_par

>>>>

      coef(h3Spat) <- p3
      # Simulate from the fitted version of Model 3
      h3_sims <- simulate(
        h3Spat, nsim = h3_nsim, format = 'data.frame'
      )

@@

      coef(h3Spat) <- p3

@@

mod3_eval_res$subset_aic <- 2 * mod3_n_params - 2 * mod3_eval_res$subset_ll

@@

\begin{tabular}{|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3}
\\
\hline
\hline
\multirow{2}{*}{Log-likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  $\Sexpr{myround(mod3_ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(h2_fit$leeFit_ll, 1)}$) &
  ($\Sexpr{myround(max(lee3_results[["all_ll_evals"]]), 1)}$)\footnotemark[2]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ &
  $\Sexpr{as.character(mod2_n_params)}$ &
  $\Sexpr{as.character(mod3_n_params)}$ \\
 Fit Parameters &
 (\Sexpr{as.character(mod1_lee_n_params)}) &
 ($\Sexpr{as.character(h2_fit$leeFit_n_params)}$) &
 ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ &
  $\Sexpr{myround(mod2_aic, 1)}$ &
  $\Sexpr{myround(mod3_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(mod2_lee_aic, 1)}$) &
  ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[2]
\\
\hline
\thead{Log-ARMA(2,1) \\ Log-likelihood} &
  $\Sexpr{myround(ARMA_benchmarks$m1, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m2, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m3, 1)}$
\\
\hline
\end{tabular}
\caption{\label{tab:likes}Log-likelihood values for each models compared to their ARMA benchmarks.
Values in parenthesis are corresponding values using \citet{lee20} parameter estimates.  $\textsuperscript{1}$The reported likelihood is an upper bound of the likelihood of the \citet{lee20} model. $\textsuperscript{2}$\cite{lee20} fit Model~3 to a subset of the data (March 2014 onward, excluding data from Ouest in 2015-2016).
On this subset, their model has a likelihood of $\Sexpr{myround(max(lee3_results$sub_ll_evals), 1)}$.
On this same subset, our model has a likelihood of $\Sexpr{myround(mod3_eval_res$subset_ll, 1)}$.
See Sec.~S5 of the supplement material for more details on estimating the likelihood of the \cite{lee20} models.
}
\end{table}

@@

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/h3_bpf_end_states.rds")) {
  h3_bpf_end_states <- readRDS("model3/run_level_3/h3_bpf_end_states.rds")
} else {
  h3_bpf_end_states <- bake(
    file = paste0("model3/", rl_dir, "h3_bpf_end_states.rds"),
    expr = {
      coef(h3Spat) <- p3
      h3_bpf <- bpfilter(h3Spat, Np = NP_BPF, block_size = 1, save_states = TRUE)
      ss <- h3_bpf@saved.states
      ss[[length(ss)]]
    },
    timing = FALSE
  )
}

@@

      # Get "noVacc" scenario parameters
      h3_S0_par <- get_model3_vacc_scenario_params(scenario = "noVacc")
      coef(h3Spat) <- p3
      coef(h3Spat)[names(h3_S0_par)] <- h3_S0_par

@@

      # Get "noVacc" scenario parameters
      h3_V1_par <- get_model3_vacc_scenario_params(scenario = "2dep")
      coef(h3Spat) <- p3
      coef(h3Spat)[names(h3_V1_par)] <- h3_V1_par

@@

      # Get "noVacc" scenario parameters
      h3_V2_par <- get_model3_vacc_scenario_params(scenario = "3dep")
      coef(h3Spat) <- p3
      coef(h3Spat)[names(h3_V2_par)] <- h3_V2_par

@@

      # Get "noVacc" scenario parameters
      h3_V3_par <- get_model3_vacc_scenario_params(scenario = "slowNation")
      coef(h3Spat) <- p3
      coef(h3Spat)[names(h3_V3_par)] <- h3_V3_par

@@

      # Get "noVacc" scenario parameters
      h3_V4_par <- get_model3_vacc_scenario_params(scenario = "fastNation")
      coef(h3Spat) <- p3
      coef(h3Spat)[names(h3_V4_par)] <- h3_V4_par
